### 2024-10-25 scripts/05-exploratory_data_analysis.qmd
scores weighted in simulation
scores weighted in simulation

```{r}
linear_model <- lm(pct ~ numeric_grade + pollscore + transparency_score + sample_size + partisan + methodology + population + race_id + stage + nationwide_batch + ranked_choice_reallocated + hypothetical, data = analysis_data)
summary(linear_model)
```

>>>>

```{r}
# Get unique population
unique_population <- unique(analysis_data$population)
print(unique_population)
```
